% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yiren Zhou}

\basicInfo{
  \email{yirenzho@andrew.cmu.edu} \textperiodcentered\
  \phone{(+1) 650-625-7637} \textperiodcentered\
  \github[yirzhou]{https://yirzhou.github.io/} \textperiodcentered\
  \linkedin[yirzhou]{https://www.linkedin.com/in/yirzhou/}
  % \location{Mountain View}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Carnegie Mellon University}, Mountain View, CA}{Sept. 2021 -- Dec. 2022}
\textit{M.S.} in Software Engineering
\datedsubsection{\textbf{University of Waterloo}, Waterloo, ON, Canada}{Sept. 2016 - Apr. 2021}
\textit{B.A.Sc.} in Computer Engineering, GPA 4.0 (91.86\%)
\begin{itemize}
  % \item {\textbf{Courses:} Algorithm Design and Analysis, Programming for Performance, Distributed Computing, Algorithms and Data Structures, Operating Systems, Compilers, Database Systems, Computer Networks}
  \item {\textbf{Award:} President's Research Award, for work on the CheckerFramework, a static analysis tool for Java code.}
\end{itemize}

\section{\faUsers\ Work Experiences}
\datedsubsection{\emph{Software Engineer Intern} \textbf{Bloomberg LP.} NY, United States}{Sept. 2020 -- Dec. 2020}
Built DataLoader, A generic C++ data fetching library compatible with various backends to serve millions of daily requests:
\begin{itemize}
  \item {Reduced network round-trips of data fetching via batching and caching.}
  \item {Drastically increased throughput by implementing multi-threading and asynchronous coroutines.}
  \item {Completed the design, implementation, testing, and deployment of the library in three months.}
\end{itemize}

\datedsubsection{\emph{Backend Developer Intern} \textbf{TextNow Inc.} ON, Canada}{Sept. 2019 -- Dec. 2019}
Re-architected QoS Packet Tester, A Go microservice that measures call quality of 700K+ Android users:
\begin{itemize}
  \item {Increased scalability by implementing concurrency in Go to allow parallel processing of thousands of user requests.}
  \item {Improved services observability with distributed tracing using OpenTelemetry and Datadog API.}
  \item {Completed the design, implementation, testing, and deployment of the microservice in three months.}
\end{itemize}

\datedsubsection{\emph{Software Engineer Intern} \textbf{Capital One Financial Corporation} ON, Canada}{Jan. 2019 -- Apr. 2019}
Developed PCI Crypto, a Python application that encrypts banking data amounting to millions of dollars in revenue.
\begin{itemize}
  \item {Leveraged multi-processing to reduce the memory consumption from O(n) to O(1) for encrypting large files.}
  \item {Enabled data owners to receive timely feedback by building an event-driven monitoring system.}
  \item {Coordinated collaboration among five teams and deployed the application to production within a two-month timeframe.}
\end{itemize}

\datedsubsection{\emph{Web Developer Intern} \textbf{Nokia Corporation} ON, Canada}{May. 2018 -- Aug. 2018}
Developed Nuage SD-WAN Portal, a web application that automates deployment and management of large-scale networks:
\begin{itemize}
  \item {Reduced the labor intensity of feature testing and development of SD-WAN portal by 70\%
        by building a proprietary tool that automates the configuration of large-scale networks.}
  \item {Built, optimized, and shipped an array of UI features (e.g., navigation bars, forms) of SD-WAN Portal in Angular.}
  \item {Completed the development and document of the tool within three months and released it to 10+ developers.}
\end{itemize}

\section{\faCodeFork\ Projects}
\begin{itemize}[parsep=0.5ex]
  \item \link[DCache]{https://drive.google.com/file/d/1Svd-wbXZiO84QmVKnKBp1cClJb2uvtWT/view?usp=sharing}: A distributed, P2P, and geospatial-aware mobile storage network.
  \item \git[Grafana Datasource Plugin for Datadog]{https://github.com/Enflick/grafana-datasource-datadog/pull/7}: An analytics and visualization software for big data.
  \item \repo[gpgodzilla]{https://pypi.org/project/gpgodzilla/}: A Python module that allows users to manipulate arbitrary-sized files with constant memory space.
  \item \link[YNOT Blogs]{http://ynotblogs.herokuapp.com/blogs}: A blogging application with user authentication, authorization, and search using NodeJS and MongoDB.
  \item \link[zhouyiren.rocks]{https://zhouyiren.rocks}: A responsive and minimalist personal website using ReactJS, React Router, and GitHub GraphQL API.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
% \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Languages: Python, Go, C++, Java, JavaScript, SQL
  \item Technologies/Tools: CMake, ReactJS, NodeJS, Docker, AWS, Git
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
