% !TEX program = xelatex


\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts
\usepackage{setspace}
\usepackage{anyfontsize}
\usepackage{hyperref}
% \hypersetup{
%     colorlinks=false,
%     % linkcolor=blue,
%     % anchorcolor=black,
%     % citecolor=black,
%     % filecolor=black,
%     % menucolor=black,
%     % runcolor=black,
%     % urlcolor=black,
%     urlbordercolor=NavyBlue
% }

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Yiren Zhou}

\basicInfo{
  \email{yirenzho@andrew.cmu.edu} \textperiodcentered\
  \github[yirzhou]{https://yirzhou.github.io/} \textperiodcentered\
  \linkedin[yirzhou]{https://www.linkedin.com/in/yirzhou/} \textperiodcentered\
  \phone{650-625-7637} \textperiodcentered\
  \location{Mountain View, CA}
}

\section{\faGraduationCap\ Education}
 {
  \fontsize{10.5pt}{2}\selectfont
  \datedsubsection{\textbf{Carnegie Mellon University}, Mountain View, CA}{08/2021 -- 12/2022}
  \textit{Master of Science in Electrical \& Computer Engineering}, GPA 3.89/4.0
  \begin{itemize}
    \item {\textbf{Relevant Courses:} Introduction to Deep Learning, Machine Learning for Signal Processing, Advanced Probability \& Statistics, Foundation of Computer Systems, Foundations in Software Engineering, Data Science for Software Engineering.}
  \end{itemize}


  \datedsubsection{\textbf{University of Waterloo}, Waterloo, ON, Canada}{09/2016 -- 04/2021}
  \textit{Bachelor of Applied Science in Computer Engineering,} GPA 4.0/4.0 (91.86\%) \newline
  \begin{itemize}
    \item {\textbf{Award:} President's Research Award, for work on the CheckerFramework, a static analysis tool for Java code.}
    \item {\textbf{Relevant Courses:} Programming for Performance, Algorithm Design and Analysis, Distributed Computing, Database Systems, Compilers, Operating Systems, Cooperative and Adaptive Algorithms, Probability Theory and Statistics.}
  \end{itemize}
  \par
 }



\section{\faUsers\ Work Experience}
 {
  \fontsize{10.5pt}{2}\selectfont
  \datedsubsection{\textbf{Coinbase Global Inc.}, San Francisco, CA, \emph{Software Engineer Intern}}{06/2022 -- 08/2022}
  Blockchain Infrastructure Products: Ethereum Ecosystem


  \datedsubsection{\textbf{Bloomberg LP.}, New York City, NY, \emph{Software Engineer Intern}}{09/2020 -- 12/2020}
  Built DataLoader, a generic C++17 data-fetching library to work with user-customizable protocols to serve millions of requests:
  \begin{itemize}
    \item {Reduced network round-trips of data fetching via batching and caching of requests.}
    \item {Increased network throughput by utilizing coroutines and event-loops.}
    \item {Delivered comprehensive tech talk on DataLoader to 50+ engineers.}
    \item {Completed full software development life cycle and deployed DataLoader in three months.}
  \end{itemize}

  \datedsubsection{\textbf{TextNow Inc.}, Waterloo, Canada, \emph{Backend Developer Intern}}{09/2019 -- 12/2019}
  Re-architected QoS Packet Tester, A microservice written in Go to measure call quality of 700K+ Android users:
  \begin{itemize}
    \item {Increased scalability by utilizing goroutines to allow parallel processing of thousands of user requests.}
    \item {Improved services observability with distributed tracing using OpenTelemetry and Datadog API.}
    \item {Completed full software development life cycle and deployed QoS Packet Tester in three months.}
  \end{itemize}

  \datedsubsection{\textbf{Capital One Financial Corporation}, Toronto, Canada, \emph{Software Engineer Intern}}{01/2019 -- 04/2019}
  Developed PCI Crypto, a Python application to encrypt banking data amounting to millions of dollars in revenue:
  \begin{itemize}
    \item {Achieved constant memory usage of encrypting large files by processing files in chunks.}
    \item {Built event-driven monitoring system to allow data owners to receive timely feedback.}
          % \item {Automated PCI files validation before file processing and encryption to reduce runtime errors.}
    \item {Coordinated collaboration among five teams and deployed PCI Crypto to production within two months.}
  \end{itemize}

  % \datedsubsection{\textbf{Nokia Corporation}, Ottawa, Canada, \emph{Web Developer Intern}}{05/2018 -- 08/2018}
  % Developed Nuage SD-WAN Portal, a application to automate deployment and management of large-scale networks:
  % \begin{itemize}
  %   \item {Reduced labor intensity of feature testing and development of SD-WAN portal by 70\%
  %         by building a proprietary tool to automate configuration of large-scale networks.}
  %   \item {Built, optimized, and shipped an array of UI features (e.g., navigation bars, forms) of SD-WAN Portal in Angular.}
  %   \item {Completed development within three months and released automation tool to 10+ developers.}
  % \end{itemize}

  \par
 }

\section{\faCodeFork\ Projects}
 {

  \fontsize{10.5pt}{1.25}\selectfont
  \setstretch{1.05}
  \href{https://github.com/yirzhou/11785-Nutrient-Estimation}{\textbf{Food Nutrient Estimator}}: (\emph{PyTorch}) Deep neural networks that estimate macroneutrients of foods from their images using Convolutional Neural Networks and multi-task learning. \\
  \href{https://github.com/pythonicmux/automated-dj-mlsp/tree/yirzhou}{\textbf{Automated Disc Jockey}}: (\emph{Python}) Algorithms to find transition points in electronic dance music using AdaBoost. \\
  \href{https://drive.google.com/file/d/1Svd-wbXZiO84QmVKnKBp1cClJb2uvtWT/view?usp=sharing}{\textbf{DCache}}: (\emph{Go, PostgreSQL, WebRTC}) A distributed, P2P, and geolocation-aware mobile storage network. \\
  \href{https://github.com/yirzhou/KVStore}{\textbf{Distributed KV Store}}: (\emph{Java, Thrift, Zookeeper}) A fault-tolerant distributed key-value store with leader election. \\
  \href{https://github.com/yirzhou/CudaCNN}{\textbf{Cuda CNN}}: (\emph{Rust, CUDA}) GPU-accelerated computation of neural network convolution. \\
  \href{https://github.com/yirzhou/IsolatedSoul/tree/main/rsbday}{\textbf{BDay.rs}}: (\emph{Rust, SQLite}) A command-line application for storing and checking birthdays that you care about. \\
  \href{https://pypi.org/project/gpgodzilla/}{\textbf{GPGodzilla}}: (\emph{Python}) A embeddable library to process arbitrary-sized files with constant memory space. \\
  \href{https://github.com/Enflick/grafana-datasource-datadog/pull/7}{\textbf{Grafana Datasource Plugin for Datadog}}: (\emph{Angular}) A Grafana plugin to display and analyze real-time data streams. \\
  % \href{http://ynotblogs.herokuapp.com/blogs}{\textbf{YNOT Blogs}}: A blogging application with user authentication, authorization, and search in \emph{NodeJS} and \emph{MongoDB}.
  \par
 }

\section{\faCogs\ Skills}
 {
  \fontsize{10.5pt}{2}\selectfont
  \onehalfspacing
  \textbf{Programming Languages}: Python, Go, Java, TypeScript, C/C++, Rust, SQL \\
  % \textbf{Scientific Computing}: PyTorch, Scikit-Learn, Scipy \\
  \textbf{Machine Learning \& Distributed Systems}: PyTorch, Scikit-Learn, Spark, Kafka, Hadoop, Zookeeper, Thrift \\
  \textbf{Tools}: AWS, Git, Linux, Docker, Jenkins, CMake
  \par
 }


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
% \item main contribution
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
